---
title: "Replication Code: Managing Churn to Maximize Profits"
author: "Aurélie Lemmens, Sunil Gupta"
date: "2020/28/01"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

\fontsize{8}{8}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# if one wants to re-run the code:
##source('main.r')

# if one only wants to print the results of the code that already ran
load('results.Rdata', verbose = T)
library(stargazer)

```

## Preamble

This document is built using R Markdown and shows how to replicate the results of Lemmens and Gupta (2020). Because the data used in the manuscript are subject to a non-disclosure agreement, this document is based on a synthetic dataset, which mimics the original observed data and preserves the relationships between variables but does not contain any disclosive records. As a consequence, results reported in this document are different from the ones reported in the paper. Please note that knitting this file might take a while when using boostrapping (i.e., B greater than 1 in the code), as the file estimates all models tested in the main manuscript, including all benchmark models. A R package is currently under development and will be released soon. You can find the latest information on wwww.aurelielemmens.com. Note that the set of results reported below are for the profit-based loss with left weighting. The code can be adapted as described in the R markdown document to display right weighting or symmetric weigting. 

The replication files include:

* the main code as R Markdown file (LemmensGupta2020_replication.rmd), 
* all functions that the R Markdown file is calling (.r files), 
* and the synthetic dataset (mysynthdata.Rdata or mysynthdata.csv).

## Table 1: Average holdout campaign profit for different estimation methods
```{r Table1, warning = FALSE, message = FALSE, echo =FALSE}
k = 4 # selects the weighting scheme, here left weighting
table1 = apply(holdoutprofit[,c(1:3,k)],2,mean,na.rm=T)
names(table1) = c("Uplift Model","Classic Loss","Reordered Classic Loss","Our Approach")
table1 = table1[c(2,3,1,4)]
table1 = t(t(table1)) 
colnames(table1) = c("Holdout Profit")
stargazer(table1,summary=F,type='text',digits = 3,digits.extra = 0, 
          title = paste0('Average campaign holdout profit for different estimation methods (',B," iterations)"))
```

## Table 2: Average holdout campaign profit for different target size determination methods
```{r Table2, warning = FALSE, message = FALSE, echo =FALSE}
k = 4 # selects the weighting scheme, here left weighting
table2 = c(mean(fixedsize.churn,na.rm=T),
                 mean(fixedsize.budget,na.rm=T),
                 mean(optsize.verbeke,na.rm=T),
                 mean(optsize.buffer,na.rm=T),
                 apply(holdoutprofit,2,mean,na.rm=T)[k])
names(table2) = c("Fixed Target Size based on Churn Rate",
                     "Fixed Target Size based on Budget",
                     "Optimized Target Size based on Verbeke",
                     "Optimized Target Size 10% Buffer",
                     "Our Approach")
table2 = t(t(table2))
colnames(table2) = c("Holdout Profit")
stargazer(table2,summary=F,type='text',digits.extra = 0,
          title = paste0('Average campaign holdout profit for different target size determination methods (',B," iterations)"))
```

## Table 3: Average holdout churn predictive accuracy for different estimation methods
```{r Table3, warning = FALSE, message = FALSE, echo =FALSE}
table3 = cbind(apply(holdoutgini,2,mean,na.rm=T),apply(holdouttdl,2,mean,na.rm=T))
rownames(table3) = c("Uplift Model","Classic Loss","Reordered Classic Loss","Our Approach")
colnames(table3) = c("Gini Coefficient","Top Decile Lift")  
table3 = table3[c(2,3,1,4),]
stargazer(table3,summary=F,type='text',digits.extra = 0,
          title = paste0('Average holdout churn predictive accuracy for different estimation methods (',B," iterations)"))
```

## Figure 2: Average holdout campaign profit as a function of target size for different estimation methods
```{r Figure2, warning = FALSE, message = FALSE, echo =FALSE, fig.width=12, fig.height=10}
par(mfrow=c(1,1))
holdoutcampaign.profit.curves = cbind(apply(holdoutcampaign.profit.curve.mysgbmodel,2,mean,na.rm=T),
                                      apply(holdoutcampaign.profit.curve.myrsgbmodel,2,mean,na.rm=T),
                                      apply(holdoutcampaign.profit.curve.myliftmodel,2,mean,na.rm=T),
                                      apply(holdoutcampaign.profit.curve.mywsgbmodel,2,mean,na.rm=T))
TS = myeval.mywsgbmodel$target.sizes
matplot(TS,holdoutcampaign.profit.curves,
        xlab = "Target Size", ylab = "Campaign Profitability",pch="",xaxt="n",
        main = paste0("Average Holdout Campaign Profit (",B," iterations)"))  
matpoints(TS,holdoutcampaign.profit.curves,col=rep(1,4),pch=1:4,type="o") 
abline(h=holdoutcampaign.profit.curves[nrow(holdoutcampaign.profit.curves),4],lty=5,col="grey")
axis(side=1, at=seq(0,nrow(mysynthdata)/3,length.out =11), 
     labels=paste0(seq(0,100,length.out =11),"%"))
legend(0,5000,c("Classic Loss","Reordered Classic Loss","Uplift","Profit Loss"),
       lty=1:4,lwd=1,pch=1:4)
```

## Figure 3: Average holdout campaign profit as a function of target size for different weighting schemes
```{r Figure3, warning = FALSE, message = FALSE, echo =FALSE, fig.width=12, fig.height=10}
par(mfrow=c(1,1))
holdoutcampaign.profit.curves = cbind(apply(holdoutcampaign.profit.curve.mywsgb3model,2,mean,na.rm=T), #symmetric
                                      apply(holdoutcampaign.profit.curve.mywsgb2model,2,mean,na.rm=T), #right
                                      apply(holdoutcampaign.profit.curve.mywsgbmodel,2,mean,na.rm=T))  #left
TS = myeval.mywsgbmodel$target.sizes
matplot(TS,holdoutcampaign.profit.curves,
        xlab = "Target Size", ylab = "Campaign Profitability",pch="",xaxt="n",
        main = paste0("Average Holdout Campaign Profit (",B," iterations)"))   
matpoints(TS,holdoutcampaign.profit.curves,col=rep(1,3),pch=5:7,type="o") 
abline(h=holdoutcampaign.profit.curves[nrow(holdoutcampaign.profit.curves),3],lty=5,col="grey")
axis(side=1, at=seq(0,nrow(mysynthdata)/3,length.out =11), 
     labels=paste0(seq(0,100,length.out =11),"%"))
legend(0,5000,c("Symmetric Weighting","Right Weighting","Left Weighting"),
       lty=1:3,lwd=1,pch=5:7)
```

## Figure 4: Average percentage customers overlapping for different estimation methods
```{r Figure4, warning = FALSE, message = FALSE, echo =FALSE, fig.width=12, fig.height=10}
plot(0:splitn,(0:splitn)*10,type="l",lty=1,xlab="Top Decile",col="grey",
     ylab="Percentage Customers Overlapping",xaxp=c(0,10,10),yaxp=c(0,100,10),
        main = paste0("Average Percentage Customers Overlapping (",B," iterations)")) 
points(0:splitn,apply(overlap.SGB.WSGB*100,2,mean,na.rm=T),type="b",lty=1,pch=1)
points(0:splitn,apply(overlap.RSGB.WSGB*100,2,mean,na.rm=T),type="b",lty=2,pch=2)
points(0:splitn,apply(overlap.LIFTrm.WSGB*100,2,mean,na.rm=T),type="b",lty=3,pch=3)
legend(0,100,c("Classic vs Profit Loss","Reordered Classic vs Profit Loss","Uplift vs Profit Loss"),
       pch=c(1,2,3),lty=1:3)
```
